---
title: "Events & Presentations"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

## Upcoming

- [3rd Marine Biodiversity Workshop: from the Sea to the Cloud](http://marinebon.org/p2p-colombia-workshop/){target="_blank"} - May 4-8, 2020, Santa Marta, Colombia. THIS EVENT IS POSTPONED DUE TO THE COVID-19 OUTBREAK AND DATES ARE TBD

## Past

- [Ocean Data Bootcamp - Gestão de dados de monitoramento costeiro](https://eqmh.github.io/Ocean_Data_Bootcamp/){target="_blank"} - July 11-14, 2022, Vitória, Brazil. 

- **Ecosystem and climate indicators for science-based decision making**. Kelly Montenero and Will Klajbor of the U. Miami CIMAS and NOAA's Atlantic Oceanographic and Meteorological Laboratory (AOML) present ecosystem and climate indicators in support of management and decision-making of marine natural resources at the [Ocean Data Bootcamp workshop](https://eqmh.github.io/Ocean_Data_Bootcamp/index.html) in Vitória, Brazil, on July 13 of 2022.
```{r, echo = F, message = F, warning = F}
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
shelf(vembedr)
embed_youtube("uKz60V0RGXo", width = 910, height = 910*360/640, frameborder = 0,
  allowfullscreen = TRUE, query = NULL)
```

- [MBON Side-event of the All-Atlantic Ocean Research Alliance 2022 Forum](https://www.aircentre.org/side-event-of-the-all-atlantic-ocean-research-alliance-2022-forum/) titled "**Coordinating marine life observations to support conservation, restoration, and equitable sustainable development**". Brasília, Brazil, June 3rd, 2022. Presentations  and panel discussion are available [here](https://www.youtube.com/watch?v=PQyE9kS3OLU&t=3s).  Organizer: [Air Centre](https://www.aircentre.org/about-us/).

- [Marine Biological Data Mobilization Workshop](https://ioos.github.io/bio_mobilization_workshop/) for publishing marine biological observation datasets to the [Ocean Biodiversity Information System - OBIS](https://obis.org/)). March 14-15, 2022.

- [From microbes to mammals: Merging in situ and spaceborne observations for monitoring life in the sea](https://bluejeans.com/s/nyhjZww92vs/). Webinar presented by Dr. Enrique Montes of [UM/CIMAS](https://cimas.rsmas.miami.edu/) for [CICESE-ULP](https://ulp.cicese.mx/en/). March 10, 2022.

- [La Red de Monitoreo de Biodiversidad Marina Polo a Polo de las Américas en apoyo a la conservación y uso sostenible de recursos marinos vivos](https://www.youtube.com/watch?v=HeqRIeB-v9o). Webinar presented by Dr. Enrique Montes of [UM/CIMAS](https://cimas.rsmas.miami.edu/) for [FIMCM ESPOL](http://www.fimcm.espol.edu.ec/). November 9, 2021.

- [AmeriGEO Week 2021 - Day 2: Health & Biodiversity:](https://vimeo.com/591158593){target="_blank"} Detecting biogeographic shifts within marine ecoregions of the Americas using dynamic satellite seascapes. See [AmeriGEO Week 2021](https://amerigeo-week-2021-amerigeoss.hub.arcgis.com/) - August 24.

- **Estimating marine biodiversity with passive acoustic monitoring**. Webinar presented by Dr. Peter Tyack of the [International Quiet Ocean Experiment (IQOE)](https://www.iqoe.org/) program. August 11, 2021.
```{r, echo = F, message = F, warning = F}
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
shelf(vembedr)

embed_youtube("lbaVgatmEP0", width = 910, height = 910*360/640, frameborder = 0,
  allowfullscreen = TRUE, query = NULL)
```

- **2021 Cohort Capstone: An investigation into the role of herbivory on coral reef recovery in Puerto Rico and the US Virgin Island**. Webinar presented on May 6, 2021.
```{r}
if (!require(librarian)){
  install.packages("librarian")
  library(librarian)
}
shelf(vembedr)

embed_youtube("T6bLoB6UrDk", width = 910, height = 910*360/640, frameborder = 0,
  allowfullscreen = TRUE, query = NULL)
```

- Panel discussion: [MarineGEO Leaders in Networked Science panel](https://twitter.com/mbonpoletopole/status/1336203878069571586){target="_blank"} - December 17, 2020 (virtual). The recording of the webinar and panel is available [here](https://smithsonian.zoom.us/rec/play/LIKD8VJ-Djax3mHkHAEMaemExsjNLwvnoeTIaT-3ie_A7_Aai7kWbLLLXPbjSmzwLN4__GUmHnjyamNw.uZYRZQojZsDcUg7Y?startTime=1608235286000&_x_zm_rtaid=4JAWT5QLQWuiqgD4iC15-Q.1608656141942.9e489a094b50da6a9f35e1e4f43dd78b&_x_zm_rhtaid=750){target="_blank"}.

- Webinar: [The Multi-Agency Rocky Intertidal Network (MARINe) Program](https://marine.ucsc.edu/){target="_blank"} - October 26, 2020, 4:00-5:10 pm EDT. The recording of the webinar is available [here](https://usf.box.com/s/9oc14djcak07sjh9hw4ekq7fxcp1b2og){target="_blank"}.

- [GEO BON Open Science Conference and All-Hands Meeting 2020](https://conf2020.geobon.org/){target="_blank"} - July 6-10, 2020 (virtual). MBON Pole to Pole presentations are available for papers on [Sampling Effort Efficieny](https://drive.google.com/file/d/1b6CRFN7Mn5D9MS8OzB6fF0BPhhfM-a66/view?usp=sharing){target="_blank"} and [Implemention of Best Practices](https://drive.google.com/file/d/1b6-DzslEnkgTqB4HwXve1lZEKLBSGGaj/view?usp=sharing){target="_blank"}.

- [AGU Fall Meeting 2019](https://www2.agu.org/fall-meeting){target="_blank"} - December 9-13, 2019, San Francisco, California. The MBON Pole to Pole absctract is available [here](https://drive.google.com/file/d/17deXPg_umFPoeYPB6QKTLDfwqv7hBUmG/view?usp=sharing){target="_blank"}.

- [10ª Semana de Integração Acadêmica da UFRJ / SIAC](http://siac.ufrj.br/){target="_blank"} - October 21-27, 2019, Rio de Janeiro, Brazil. A poster on sandy beach biodiversity is available [here](https://drive.google.com/file/d/1fTgRFdOIGuESTIFHzMmO-nYa0KF4DOMc/view?usp=sharing){target="_blank"}

- [OceanObs'19](http://www.oceanobs19.net/){target="_blank"} - September 16-20, 2019. Check out posters on [MBON Pole to Pole](https://drive.google.com/file/d/1AWpEQSBzLOAGapNOh1J3KQwkB4GTVFXQ/view?usp=sharing){target="_blank"} and [biodiversity monitoring and citizen science](https://drive.google.com/file/d/1BHuRr4WBTZIqBvBYphcUs9birViUnN5X/view?usp=sharing){target="_blank"}.  

- [MBON Pole to Pole presentation](https://usf.app.box.com/s/08569c61yektdv3odcgwuy5x1cmvuy8p){target="_blank"} for the Global MBON monthly webinar - September 9, 2019. 

- [2019 AmeriGEO Week](https://www.amerigeoss.org/amerigeoss-events/amerigeoss-week-2019){target="_blank"} - August 19-23, 2019, Lima, Peru. The MBON Pole to Pole will be represented at the AmeriGEO Week by [IMARPE](http://www.imarpe.gob.pe/imarpe/){target="_blank"}

- [XIII Biofouling, Benthic Ecology and Marine Biotechnology Meeting](https://xiiibioinc.wixsite.com/xiiibioinc){target="_blank"} - August 5-9, 2019, Arraial do Cabo, Rio de Janeiro, Brazil. The MBON Pole to Pole poster is available [here](https://drive.google.com/file/d/1AVl5loMTuzkE_xdBw9d-J7HNMojO_v9F/view?usp=sharing){target="_blank"}

- [XXXIX Congreso de Ciencias del Mar “Recuperación y protección de la biodiversidad en un escenario de cambio global”](https://www.congresocienciasdelmar.cl/){target="_blank"}<br>
May 27-31, 2019, Iquique, Chile. The MBON Pole to Pole absctract is available [here](https://drive.google.com/file/d/1V5ZDpoSoY9vU3MFXR6tVSro6Uaab4PZh/view?usp=sharing){target="_blank"}. Presentation slides are also available [here](https://drive.google.com/file/d/1V3j9ZRAJg0ycXsPYmUWyNw4Hx7trJLeW/view?usp=sharing){target="_blank"}.

- [NASA Biodiversity and Ecological Forecasting Meeting](https://drive.google.com/file/d/1fxq8MvqTIWO_N1hUmw11F4L4u6AsyNuG/view?usp=sharing){target="_blank"}<br> 2019-05-22 in Washington DC, USA

- [2nd Marine Biodiversity Workshop: from the Sea to the Cloud](https://marinebon.github.io/p2p-mexico-workshop/){target="_blank"}<br>
  2019-04-02 in Puerto Morelos, Mexico
  
- [American Gephysical Union Fall Meeting 2018](https://drive.google.com/file/d/1YFOOYFZNmNTGzK3BRestIS1RltkZImEu/view?usp=sharing){target="_blank"}<br>
  2018-12-10 in Washington DC, USA

- [Marine Biodiversity Workshop: from the Sea to the Cloud](https://marinebon.github.io/p2p-brazil-workshop/){target="_blank"}<br>
  2018-08-06 in São Sebastião, Brazil


